GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-10-11 paper/kbanotebook2013/content/implementation.tex
small changes in the algorithm

\begin{algorithm}
  \textbf{Given a set of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
  \textbf{Set of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \begin{algorithmic}[1]
    \FOR{$si \in \mathcal{S}$}
    \FOR{$s \in si$}
    \IF{$ check\_one\_of\_the\_patterns$}
    \STATE Emit(sentence, pattern)
  \ENDIF
\ENDFOR
\ENDFOR
\end{algorithmic}
\end{algorithm}

@@

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next we will explain the patterns with more details, a brief
example can be found in Figure~\ref{fig:pattern}.

\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
pattern: \textless \texttt{PER, FounderOf, ``founder'', right, ORG}\textgreater. PER means 
that the entity we are finding slot values for is a PER entity; FounderOf 
means this is a pattern for FounderOf slot. Founder is the anchor word we are 
trying to match in the sentence text; right means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

\textbf{Slot value tagged as noun phrase by OpenNLP:} \textless \texttt{PER, AwardsWon, ``awarded'', 
right, NP}\textgreater, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the ``awarded'' since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

\textbf{Slot value of time phrases, hard coded:} \textless \texttt{PER, DateOfDeath, ``died'', right, 
``last night''}\textgreater. In this pattern, ``last night'' means we are looking for 
exactly the phrase ``last night'' to the right of ``died''. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.

>>>>

\begin{algorithm}
  \textbf{List of entities $\mathcal{E} = \{e_0, \ldots, e_{170}\}$}\\
  \textbf{List of Streamitems $\mathcal{S} = \{s_0, \ldots, s_{|\mathcal{S}|}\}$}\\
  \textbf{List of patterns $P = \{p_0, \ldots, p_{|P|}\}$}\\
  \begin{algorithmic}%[1]
    \FOR{$si \in \mathcal{S}$}
      \FOR{$sentence \in si$}
        %%\IF{check\_pattern(sentence, pattern)}
        \FOR{$pattern \in P$}
          \IF{Satisfies($sentence$, $pattern$)}
            \STATE Emit($sentence$, $pattern$)
          \ENDIF
        \ENDFOR
      \ENDFOR
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

@@

The first value, $p_1$ represents the type of entity. These entity types are in
the set $\{ \text{\tt FAC}, \text{\tt ORG}, \text{\tt PER} \}$ where \texttt{FAC}
represents a type of facility, \texttt{ORG} represents an organization and \texttt{PER}
represents a person.
The $p_2$ represents a slot name.
A list of slot names is present in Table~\ref{table:slotNameOntology}.
The third element $p_3$ is the pattern content. This is a string found in the sentence.
The extractor looks for this exact string or pattern in a sentence.
The pattern evaluator uses a direction (\texttt{left} or \texttt{right}) found in
$p_4$ to explore sentence.
The final element $p_5$ represent the slot value of a pattern. Thois
%When we match one pattern, we match all the 
%fields except the third field, which is extracted as the final result.
The type of slot value may be the entity 
type tagged by Lingpipe, a noun phrase (\texttt{NP}) tagged by OpenNLP or a hard-coded phrase. 
For these three kinds of patterns, we implement them in different 
ways accordingly. Next, we will explain the patterns with more details, an
example can be found in Figure~\ref{fig:pattern}.

\textbf{Slot value type, tagged by Lingpipe:} For slot FounderOf, we have this
pattern: $\langle$ \texttt{PER, FounderOf, ``founder'', right, ORG} $\rangle$. PER means 
that the entity we are finding slot values for is a PER entity; FounderOf 
means this is a pattern for FounderOf slot. Founder is the anchor word we are 
trying to match in the sentence text; right means that we are going to the 
right part of the sentence to match the pattern and find the slot value; ORG 
means the slot value should be a ORG entity.

\textbf{Slot value tagged as noun phrase by OpenNLP:} $\langle$ \texttt{PER, AwardsWon, ``awarded'', 
right, NP}$\rangle$, NP meaning noun phrase. This pattern can be interpreted 
as that we are looking for a noun phrase after the ``awarded'' since that noun 
phrase could possibly represent an award. Since titles and awards are usually 
not the Lingpipe entities, we use the OpenNLP noun phrase chunker to fetch the 
noun phrases.

\textbf{Slot value of time phrases, hard coded:} $\langle$ \texttt{PER, DateOfDeath, ``died'', right, 
``last night''}$\rangle$. In this pattern, ``last night'' means we are looking for 
exactly the phrase ``last night'' to the right of ``died''. This pattern is 
inspired by the intuition that in news articles, people often mention that 
somebody died last night instead of mentioning the accurate date information 
and Lingpipe tends not to tag phrases like ``last night'' as a DATE entity.
